---
title: "IMDB"
author: "Ben Baumer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IMDB}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Since you will be downloading lots of data, you may want to specify a directory to store it all

```{r}
library(imdb)
```

Next, we have to make a connection to a SQL server. Note that the `imdb` database should be created ahead of time. 

```{r, eval=FALSE, message=FALSE}
if (require(RPostgreSQL)) {
  # must have pre-existing database "imdb"
  db <- src_postgres(host = "localhost", user = "postgres", password = "postgres", dbname = "imdb_fresh")
}
```

```{r, eval=FALSE}
imdb <- etl("imdb", db = db, dir = "~/dumps/imdb/")
```

Download the data -- this may take a while. There are 49 files that take up approximately 1.6 GB on disk.

```{r, eval=FALSE}
imdb %>%
  etl_extract()
```

Now process these raw data files and pump them into this `db`. This can take a loooong time. For the full set of files it took about 54 hours!

```{r, eval=FALSE}
imdb %>%
  etl_load()
```