---
title: "IMDB"
author: "Ben Baumer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IMDB}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Roll your own IMDB SQL database

```{r, message=FALSE}
library(imdb)
```

Since the IMDB is very large (many gigabytes), it is best to store the data in a persistent SQL database. By default, `etl` will create an `RSQLite` for you in a temp directory -- but this is not a very safe place to store these data. Instead, we will connect to an existing (but empty) PostgreSQL database. 

```{r, eval=FALSE, message=FALSE}
if (require(RPostgreSQL)) {
  # must have pre-existing database "imdb_fresh"
  db <- src_postgres(host = "localhost", user = "postgres", password = "postgres", dbname = "imdb")
}
```

Since you will be downloading lots of data, you will probably want to specify a directory to store the raw data (which will take up several gigabytes on disk). Again, `etl` will create a directory for you if you don't, but that directory will be in a temp directory that is not safe. 

```{r, eval=FALSE}
imdb <- etl("imdb", db = db, dir = "~/dumps/imdb/")
```

### Performing the ETL steps

The first phase is to **E**xtract the data from IMDB. This may take a while. There are 49 files that take up approximately 2 GB on disk. By default, only the `movies`, `actors`, `actresses`, and `directors` files will be downloaded, but even these take up more than 500 MB of disk space. 

```{r, eval=FALSE}
imdb %>%
  etl_extract(tables = c("movies"))
```

Mercifully, there is no **T**ransform phase for these data. However, the **L**oad phase can take a loooooong time. 

The load phase leverages the Python module `IMDbPy`, which also has external dependencies. Please see the [.travis.yml](https://github.com/beanumber/imdb/blob/master/.travis.yml) file for a list of those dependencies (on Ubuntu -- your configuration may be different). 

You'll want to leave this running overnight. To load the full set of files it took about 54 hours!

```{r, eval=FALSE}
imdb %>%
  etl_load()
```

## Query the database

Once everything is completed, you can query your fresh copy of the IMDB.

```{r, eval=FALSE}
movies <- imdb %>%
  tbl("title")
movies %>%
  filter(title == "Star Wars")
```

